Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/experiments.tex
more edits!

The gold standard for comparison was derived from the testing set in each
dataset. To make the comparison as fair as possible among models, ancestors of
observed 
nodes in the label hierarchy were ignored, observed nodes were considered
positive and descendents of observed nodes were considered to be negative. In
particular, since the sLDA model does not enforce the hierarchical constraints,
its performance was found to be so poor on joint prediction that it was not
included. 
The models can be compared on a more equal footing by considering only on the observed labels
as being positive despite the fact that ancestors must also be positive. The gold standard 
defined in this way will likely inflate the number of
false positives because the labels applied to any particular document are usually not as complete as they could be. 
ICD-9 codes lack sensitivity and their use as a
gold standard could lead to correctly positive predictions being labeled as false positives\citep{Birmetal2005}.
However, given that the label space is often large (as in our examples) it is a moderate assumption that
erroneous false positives should not skew results significantly.

>>>>

The gold standard for comparison was derived from the testing set in each
dataset. To make the comparison as fair as possible among models, ancestors of
observed nodes in the label hierarchy were ignored, observed nodes were
considered positive and descendents of observed nodes were considered to be
negative. In particular, since the sLDA model does not enforce the hierarchical
constraints, its performance was found to be so poor on joint prediction that
it was not included. The models can be compared on a more equal footing by
considering only on the observed labels as being positive, despite the fact
that, following the hierarchical constraints, ancestors must also be positive.
Such a gold standard will likely inflate the number of false positives because
the labels applied to any particular document are usually not as complete as
they could be.  ICD-9 codes, for instance, lack sensitivity and their use as a
gold standard could lead to correctly positive predictions being labeled as
false positives\citep{Birmetal2005}. 
However, given that the label space is often large (as in our examples) it is a
moderate assumption that erroneous false positives should not skew results
significantly.
